
\documentclass[10pt]{article}

% Package used to manipulate the document header and footer
\usepackage{fancyhdr}

\pagestyle{fancy}
\rhead{HPS-NOTE XXX}
\cfoot{\thepage}
\lhead{}
\renewcommand{\headrulewidth}{1pt}

\begin{document}

\begin{center}
\Large
\textbf{Heavy Photon Search Core Principles and Collaboration Guidelines}
\end{center}

\normalsize
\tableofcontents
\clearpage

\section{Core Principles}

\subsection{Respect and support members of the collaboration}
\begin{itemize}
    \item The collaboration is composed of members from different backgrounds whose
    diverse perspectives must be respected. 
    \item Acknowledge the privilege and power you hold and use it to empower 
    and amplify voices that are being excluded. 
    \item Criticism should be constructive and delivered in a respectful way
    with the aim of creating positive discussion. 
    \item Collaborators should feel supported in all situations; enabling 
    them to be creative in their ideas and solutions and thrive in our 
    community. 
    \item Avoid judging, discriminating, or making unwelcome jokes or disparaging remarks based on stereotypes
\end{itemize}

\subsection{Commit to openness}
\begin{itemize}
    \item Set aside implicit biases when hearing different perspectives, ideas and solutions.   
    \item Take it upon yourself to eliminate particular challenges or barriers to success that colleagues may face as members of under-represented groups
\end{itemize}

\subsection{Recognize that intent does not equate to impact}
\begin{itemize}
    \item The intention of your comments may not be to hurt but that does not
    mean that they didn't have a negative impact. 
\end{itemize}


\section{Guidelines}

\subsection{All spaces}
\begin{itemize}
    \item Be welcoming and open-minded.  Recognize that members of the 
      collaboration may not have the same experience level or background as 
      you, but that doesn't mean their ideas should be ignored. 
    \item New members of the collaboration should be welcomed and encouraged 
      to express themselves and their ideas. 
    \item All interactions with collaborators should be done with respect and 
      empathy. Disagreements are expected to happen.  However, when a disagreement
      occurs, try your best to understand the other perspective before addressing 
      them.  The aim should be to promote a collegial atmosphere in which 
      everyone is comfortable voicing their ideas and engaging in coversation.
    \item Actively work to improve the collaboration. We should all strive to 
      encourage positive, respectful behaviour while discouraging negative 
      behavior. Intervene when you see behavior that violates our community 
      standards. 
    \item All HPS related activies should be made inclusive. For example, 
      make sure new collegues are aware of unstructured activies such as lunches, 
      dinners and coffee breaks.
    \item If a colleague tells you your words or actions have had a negative 
      impact, strive to understand their perspective.  Understand why your words
      or actions had a negative impact.  The burden should not be on your colleague 
      to explain the issue to you. 
    \item During meetings, actively work to give positive feedback on a talk 
      or discussion.  Minimize the amount of negative impact that is given during
      a meeting and instead save it for offline. 
\end{itemize}

\subsection{Online}
\begin{itemize}
    \item When communicating online via a platform like Slack, make sure to 
    be clear and stay on topic.  Conveying tone and expressing sarcasm is much
    harder to do when communicating via text and is often misinterpreted. Take 
    more care to understand how your message will be perceived when 
    communicating online.
    \item Strive to improve discussions.  Engage in discussions with the 
    intent of having a positive impact on it.  
\end{itemize}


\section{Unacceptable Behavior}
  \begin{itemize}
    \item Discrimination and hate speech of any form. This includes comments
      related to race, color, religion, gender, gender identity and expression, 
      sexual orientation, disability, physical apperance or any other personal 
      characteristics. 
    \item Bullying behavior and harrasmenet. Any behavior that makes meetings 
      or any other form of communication uncomfortable and unwelcoming is not
      allowed.  This is especially important as we strive to create an 
      inclusive environment for our more vulnerable collaborators. 
    \item Retaliatory behavior against anyone who reported a violation. 
  \end{itemize}

\section{Enforcement}

\end{document}
